%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer \& Analyst} % Job title
    {Sogema Technologies Inc} % Organization
    %{Montreal, Canada} % Location
    {Sept. 2016 - Present} % Date(s)
    {Montreal, Canada} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Mid-large size company for building and deploying software solutions to governments}
        \item {Participated in the analysis of business requirements and high-level solution architecture}
        \item {Aided in structuring and implementing the solutions, infrastructures, development process/workflows testing processes, versioning flows and quality assurance.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {CTO and Co-founder} % Job title
    {Enkidoo Technologies Inc.} % Organization
    {Aug. 2015 - Feb. 2016} % Location
    {Montreal, Canada} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item{ A start-up with five employees and two significant outside investors, creating a specialized suite of inventory management applications for mid-sized firms. }
        \item{ Designed a probabilistic forecasting model; then developed a fully-integrated real-time inventory optimization software to meet service level requirements at minimal costs  }
        \item{ Architected and implemented solutions, infrastructures, development process/workflows testing processes, versioning, quality control and continuous integration. }
        \item{ Executed business and supply chain analysis }
        \item{ Built various system integrations (ERPs, CRMs, E-Commerce, Vendors, 3PLs) }
        \item{ Management of four interns / employees (hiring, training, performance reviews)  }
        \item{ Demos and meetings with investors, board members and clients. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Netsuite ERP Developer} % Job title
    {ERP Guru} % Organization
    {Jan - Aug. 2015 \& May - Sept. 2016} % Location
    {Montreal, Canada} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{ Spearheaded software portions of two large projects (customization and implementation) }
        \item{ Second ever intern to be offered part-time position immediately after internship }
        \item{ Maintained higher than usual billability; often completely booked many weeks in advance }
        \item{ Architected smaller solutions and advised on technical aspects of many larger projects }
        \item{ Met with clients for requirements gathering and software demos }
        \item{ Conducted inventory optimization seminar and demo for entire company }
        \item{ Worked with approximately 15 clients across wide range of business sectors }
        \item{ Built software solutions, test plans, software implementation procedures }
      \end{cvitems}
    }

\end{cventries}
